Aldebaran~b's temperate past uncovered in planet search data

### 2018-07-14 paper/aldebaran.tex
Closes #10
Clarify that "CARMA" in Fig 4 caption refers to our analysis, not the 
radio telescope.
addressed scaling relation comment by referee

While the accuracy of these scaling relations is still a matter of ongoing work \citep[e.g.,][]{2017ApJ...844..102H}, stellar parameters can be estimated by comparing observables to parameters from models of stellar evolution.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{psd-zoom.pdf}
\caption{CARMA-derived power spectral density from archival and SONG RV observations of Aldebaran, showing the clear peak at around 2\,\muHz. The dark and light shaded regions represent $1\,\sigma$~and $2\,\sigma$ posterior probability contours. }
\label{psd}
\end{figure}

>>>>

The accuracy of these scaling relations is still a matter of ongoing work, but recent comparisons using Gaia parallaxes has shown encouraging agreement for red giants \citep[e.g.,][]{2017ApJ...844..102H,zinn18}. \citet{viani17} recently used models to demonstrate that the \numax\ scaling relation may show a dependence on the mean molecular weight. However, this effect is typically at the 0.01--0.02\,dex level for red giants, which is a factor $\sim$\,2--4 smaller than our measurement uncertainties (see Section 4) and thus does not significantly affect the conclusions in this paper.

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{psd-zoom.pdf}
%
\caption{Power spectral density derived from the CARMA analysis of archival and
SONG RV observations of Aldebaran, showing the clear peak at around 2\,\muHz.
The dark and light shaded regions represent $1\,\sigma$~and $2\,\sigma$
posterior probability contours. }
%
\label{psd}
\end{figure}
